\section{Professional Experience}

\resumeSubHeadingListStart

    \resumeSubheading
        {Rippling}{\faCalendar[regular] 2023 -- Present}
        {Senior Software Engineer - Reports Platform}{\faMapMarker* \ Montreal, Quebec, Canada}
        \resumeItemListStart
            \resumeItem{Spearheaded the adoption of domain-driven hexagonal design through engaging lunch-and-learn presentations, comprehensive documentation, a demo repository, and hands-on implementation guidance, complemented by personalized coaching and code review feedback.}
            \resumeItem{Implemented a polling mechanism on the Front-End for a mission-critical workflow, boosting the success rate from approximately 69\% to an impressive 99\% by effectively mitigating API Gateway timeout issues.}
            \resumeItem{Identified and resolved front-end performance bottlenecks in an integral reports page that caused freezing, leveraging memoization techniques, component optimization, and refined data processing algorithms to deliver a seamless user experience.}
            \resumeItem{Developed new features and troubleshot complex issues for high-value EOR and Partner Administrator reporting accounts, ensuring flawless functionality and an exceptional user experience.}
            \resumeItem{Authored multiple team-focused, and organization-wide RFCs for both the Front-End and Back-End to strategically plan for the long-term scalability and maintainability of the platform, making significant contributions to the overarching product strategy and technical roadmap.}
            \resumtItem{Recognized for being proactive and assertive in identifying and addressing potential issues, and always being a supportive and pleasant colleague.}
        \resumeItemListEnd

    \resumeSubheading
        {Twitch}{\faCalendar[regular] 2021 -- 2023}
        {Software Engineer – Web Video Clients}{\faMapMarker* \ Montreal, Quebec, Canada}
        \resumeItemListStart
            \resumeItem{Resolved critical Nvidia Shield video issues, saving the company upwards of \textdollar 1M annually.}
            \resumeItem{Identified a strategic opportunity for potential annual savings of \textdollar 1M+ by conducting in-depth research and data gathering on the HEVC/h.265 codec for the Twitch platform, as confirmed by data science and BI teams, showcasing proactive analysis and cost-saving insights.}
            \resumeItem{Boosted video player unit test coverage by 30\%, uncovering approximately 30 previously unidentified bugs in the process.}
            \resumeItem{Played a key role in a week-long hackathon, successfully releasing around 20M frozen usernames back into the user space.}
            \resumeItem{Implemented Nx monorepo tooling and re-architected major components of the living room video testing application to support multiple platforms.}
            \resumeItem{Collaborated with application teams to address platform issues and designed Cloudwatch dashboards for living room platforms, streamlining monitoring and management.}
            \resumeItem{Engineered a significant portion of the peer-to-peer broadcasting SDK, introducing design patterns and preparing the repository for open-source contributions, while authoring the majority of CI in Github Actions and developing customized automation tooling for deep end-to-end coverage insights.}
        \resumeItemListEnd

    \resumeSubheading
        {Lightspeed Commerce}{\faCalendar[regular] 2019 -- 2021}
        {Software Developer II}{\faMapMarker* \ Montreal, Quebec, Canada}
        \resumeItemListStart
            \resumeItem{Developed a desktop application and driver to interface with printer hardware, successfully reducing aggregate support volume by nearly 15\% and saving significant costs.}
            \resumeItem{Spearheaded the development of a production-ready Electron application, providing low-level control over thermal printers, computer monitors, and other POS hardware, enabling retailers to swiftly detect and address hardware issues.}
            \resumeItem{Undertook a challenging migration of a 15-year-old legacy monolith to Typescript, optimizing code quality, enhancing maintainability, and promoting efficient cross-team collaboration.}
            \resumeItem{Earned Scrum Master Certification and assumed the role of Scrum Master for a newly formed 13-person team, driving agile methodologies and maximizing team productivity.}
            \resumeItem{Distinguished as a Squad Lead, showcasing exceptional leadership and communication skills by documenting progress, updating stakeholders, and ensuring project success as the team's point of contact.}
            \resumeItem{Exercised exceptional project management skills by orchestrating scrum ceremonies and events, streamlining team collaboration, and boosting productivity.}
        \resumeItemListEnd

    \resumeSubheading
        {NewKnow}{\faCalendar[regular] 2018 -- 2019}
        {Full Stack Developer}{\faMapMarker* \ Montreal, Quebec, Canada}
        \resumeItemListStart
            \resumeItem{Led the development of the front-end application for the company's latest product, delivering innovative solutions on time and within the agreed scope.}
            \resumeItem{Built new, flexible components that enabled clients to create customized training modules tailored to their unique requirements, enhancing user experience and engagement.}
            \resumeItem{Contributed significantly to the product roadmap and feature conception by leveraging extensive industry experience and monitoring emerging trends and user needs.}
            \resumeItem{Developed the application using an event-sourced microservices architecture, ensuring high scalability, flexibility, and resilience.}
        \resumeItemListEnd

    \resumeSubheading
        {SweetIQ}{\faCalendar[regular] 2015 -- 2018}
        {Intermediate Software Developer (2017 -- 2018)}{\faMapMarker* \ Montreal, Quebec, Canada} \\
        \vspace{4pt}
      	\textit{\small Junior Software Developer (2015 -- 2017)} \\
      	\vspace{-7pt}
        \resumeItemListStart
            \resumeItem{Rapidly promoted from Junior to Intermediate Software Developer, reflecting exceptional performance and contributions to the company's success.}
            \resumeItem{Orchestrated the development of an award-winning enterprise solution, serving dozens of clients and generating multi-million-dollar revenue, surpassing expectations.}
            \resumeItem{Engaged in the development of high-traffic customer-facing products, catering to hundreds of thousands of users per month and ensuring client satisfaction through timely delivery and top-notch support.}
            \resumeItem{Conducted on-site visits to enterprise clients, providing technical support and elevating overall satisfaction levels.}
            \resumeItem{Collaborated closely with product and design teams, ensuring consistent and seamless delivery of high-quality products.}
            \resumeItem{Mentored and guided junior developers and freelancers, empowering them to become self-sufficient contributors to the team's success and ensuring seamless team collaboration.}
            \resumeItem{Strategized and designed roadmap items to steer the product towards a profitable and scalable future, while contributing to architectural design decisions, such as crafting the Store Locator Solution in line with business objectives.}
            \resumeItem{Brought a unique sales-oriented mindset to all development and product meetings, fostering a culture of success and client satisfaction.}
        \resumeItemListEnd

\resumeSubHeadingListEnd
